Interisland movements and oceanic swimming of woodland caribou in Newfoundland

### 2020-05-15 paper/manuscript.Rmd
EVW comments

@@

Forage limitation may be the ultimate explanation for caribou swimming between
oceanic islands, but a number of proximate mechanisms remain untested. Our
observations of caribou swimming in the ocean lead to five questions for future
research:

>>>>

<!-- That first paragraph would benefit from a bit of signpost at its end to
let us know what kind of ideas you're going go talk about near the end. -->

@@

Forage limitation may be the ultimate explanation for caribou swimming between
oceanic islands, but a number of proximate mechanisms remain untested. Our
observations of caribou swimming in the ocean lead to five questions for future
research:
<!-- a) For the questions that arise, maybe try to generalize the language a bit
so that they are a bit broader: caribou as model, but emphasize the
ecological/evolutionary process it will comment on. 
b.) Consider tweaking the
intro the the questions less as 'someone could do this' as something along the
lines of : this has ignited in us the idea that we can tailor our data
collection in our closely studies system to access some of these questions. -->
